---
title: "shrimp_nutrient_pollution"
author: "Gage Clawson (NCEAS, UCSB, OHI)"
date: "12/22/2020"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: yes
    includes: 
toc: true
---

This markdown uses models and species specific parameters from the paper *Aquaculture Production is a Large, Spatially Concentrated Source of Nutrients in Chinese Freshwater and Coastal Seas* (2020 Wang et al)

## Set up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(sf)
library(raster)
library(readr)
library(data.table)

source(here("_spatial/template_raster.R"))

path_prep <- "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/shrimp"
path_final <-"/home/shares/food-systems/Food_footprint/all_food_systems/datalayers"
path_pre <- "/home/shares/food-systems/Food_footprint/all_food_systems/predatalayers"

production <- read_csv(file.path(path_prep, "shrimp_farm.csv"))
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)
```

shrimp N/P pollution values

N: 57 kg/tonne of growth
P: 9.2 kg/tonne of growth

Steps: 
1. Multiply tonnes production by 0.95 (this corrects for the growth that occurs outside the seapen on land), this is the value Lex uses
2. Then multiply growth by the N value and the P value
3. We report in total excess nutrients: Sum the N and P values.
4. We report in tonnes, so divide by 1000. 

```{r}

shrimp_pollution <- production %>%
  dplyr::mutate(prod_growth = tonnes_production*0.95) %>%
  dplyr::mutate(prod_growth_N_poll = prod_growth*57,
                prod_growth_P_poll = prod_growth*9.2) %>% ## in kg pollution now
  # dplyr::mutate(PO4eq_kg = prod_growth_N_poll*0.42 + prod_growth_P_poll*3.07) %>% cut (01/14/2021)
  dplyr::mutate(N_P_tonnes = (prod_growth_N_poll + prod_growth_P_poll)/1000,
                N_tonnes = prod_growth_N_poll/1000,
                P_tonnes = prod_growth_P_poll/1000) %>%
  dplyr::select(x, y, N_P_tonnes, N_tonnes, P_tonnes)

sum(shrimp_pollution$N_P_tonnes) # 320370
sum(production$tonnes_production) # 5094133

## save to dataprep folder with the correct naming conventions: 
write.csv(shrimp_pollution, file.path(path_prep, "shrimp_nutrient.csv"))


## save N + P layer
N_P_df <- shrimp_pollution %>%
  dplyr::select(x,y, N_P_tonnes)

final_rast <- rasterFromXYZ(N_P_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 320370

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 320370
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_final, "marine_shrimp_aquaculture_meat_nutrient.tif"), overwrite = T)


## save N layer
N_df <- shrimp_pollution %>%
  dplyr::select(x,y, N_tonnes)

final_rast <- rasterFromXYZ(N_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 275847.3

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 275847.3
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_pre, "marine_shrimp_aquaculture_meat_nutrientN.tif"), overwrite = T)



## save P layer
P_df <- shrimp_pollution %>%
  dplyr::select(x,y, P_tonnes)

final_rast <- rasterFromXYZ(P_df, crs = food_crs)
crs(final_rast)
plot(final_rast)
final_rast
cellStats(final_rast, "sum") # 44522.72 

final_area_fix <- final_rast/raster::area(final_rast)

final_rast_proj <- projectRaster(final_area_fix, food_raster, method = "ngb")

final_rast <- final_rast_proj*raster::area(final_rast_proj)
cellStats(final_rast, "sum") # 44522.72
final_rast

## Save to datalayers 
writeRaster(final_rast, file.path(path_pre, "marine_shrimp_aquaculture_meat_nutrientP.tif"), overwrite = T)

```

