---
title: "Modeling salmon production (tonnes) to total number"
author: "Juliette Verstaen"
date: "1/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries and paths}
library(dplyr)
library(tidyr)
library(data.table)
library(countrycode)
library(readxl)
library(stringi)
library(stringr)
library(ggplot2)
library(readr)

raw_path <- "/home/shares/food-systems/Food_footprint/_raw_data/"
```

## About 

Calculating conversion factor converting production of salmon reported in tonnage to the number of individual salmon.

## Data

1. For this we are going to use the data found [here](https://www.ssb.no/en/statbank/table/09259/), which documents for each county: 
- The stock number as of Jan 1st
- Supplies - how many additional fish were added
- Delivered for sale - how many fish were removed for consumption
- Loss - number of fish died
- The stock number as of Dec 31st
- Percent loss

2. [Aquaculture sales](https://www.ssb.no/en/statbank/table/07326)


## Methods

### Norwegian Fisheries Directorate data wrangling
First we're going to read in the production data we have, and keep all the years. 
```{r wrangling production data}
nor_prod <- read_csv(here("aquaculture/marine/salmon/salmon_farm/data/norway_mariculture_gf.csv")) %>% 
  filter(species == "Salmon") %>% 
  dplyr:: select(year, region,variable, value) %>% 
  spread(variable, value) %>% 
  rename(salmon_tonnes = tonnes_fish) %>% 
  mutate(Stock_Jan1_count = Stock_Jan1_count*1000,
         loss_count = loss_count*1000,
         stock_dec_31_count = stock_dec_31_count*1000,
         delivered_for_sale_count = delivered_for_sale_count*1000,
         supplies_count = supplies_count*1000)

```

Checking the total annual sum of salmon production in Norway
```{r annual totals}
## combine them all together for total salmon in all of Norway.
nor_pro_county<- nor_prod %>% 
  group_by(year) %>% 
  summarize(total_salmon_tonnes = sum(salmon_tonnes))

nor_pro_county
```

Because graphs are fun!!
```{r graph production by region}
# graph!
plot <- ggplot(nor_prod)+
  geom_line(aes(x=year, y = salmon_tonnes, color=region))+
  ggtitle("Salmon Production in Norwegian Counties") +
  ylab("Tonnage of Salmon") +
  xlab("Year") +
  theme_classic() 
plot

```

###SSB Data wrangling

**Pulling out Nord and Sor** 
Up until 2017 Trøndelag was Nord-Trøndelag and Sør-Trøndelag. Since the production data we have combines both of these counties during that time, we are going to do the same here to avoid unnecessary errors in our modeling. Here I pull out that data to work on it so I can better see what's happening. 

```{r nord_tron and sor_tron wrangling}

trond <- nor_prod %>% 
  filter(region == "Nord-Trøndelag" | region == "Sør-Trøndelag" | region == "Trøndelag") %>% 
  group_by(year) %>%
  
  mutate(t_stock = sum(Stock_Jan1_count),
         t_prod = sum(salmon_tonnes),
         t_loss_count = sum(loss_count),
         t_stock_dec_31_count = sum(stock_dec_31_count),
         t_sale = sum(delivered_for_sale_count),
         t_supplies_count = sum(supplies_count)) %>% 
  
  dplyr::select(year, t_stock, t_prod, t_loss_count, t_stock_dec_31_count, t_sale, t_supplies_count) %>% 
  
  rename(Stock_Jan1_count = t_stock,
         salmon_tonnes = t_prod,
         delivered_for_sale_count = t_sale,
         stock_dec_31_count = t_stock_dec_31_count,
         loss_count = t_loss_count,
         supplies_count = t_supplies_count) %>% 
  
  mutate(region = "Trøndelag") %>% 
    unique() 

```

**Finishing up SSB data wrangling**
```{r finalizing ssb data wrangling}
nor_prod <- nor_prod %>% 
  ### get rid of the Trondelag, Sor, and Nord that we will add back in consolidated
  filter(region != "Nord-Trøndelag" & region != "Sør-Trøndelag" & region != "Trøndelag") %>%
  bind_rows(trond)

plot <- ggplot(nor_prod)+
  geom_line(aes(x=year, y = salmon_tonnes, color=region))+
  ggtitle("Salmon Production in Norwegian Counties") +
  ylab("Tonnage of Salmon") +
  xlab("Year") +
  theme_classic() 
plot

```

###Combine both data sets


```{r combine data sets}
all_salmon <- nor_prod %>% 
  mutate(salmon_kg = salmon_tonnes*1000,
         avg_harvest_wgt_kg = salmon_kg/delivered_for_sale_count,
         mortality_rate = loss_count/(Stock_Jan1_count)) 
#%>%   filter(num_loss != is.na(num_loss))

write.csv(all_salmon, file = "data/all_salmon_norway.csv")
```

Check to see if the math for adding the number of salmon at the end of the year matches the reported values
```{r}
sal_check <- all_salmon %>% 
  mutate(test = Stock_Jan1_count  + supplies_count - loss_count - delivered_for_sale_count,
         diff = test - stock_dec_31_count,
         perdiff = diff/stock_dec_31_count)
```

Some of these values are off by either 1000 or 2000 fish (weird that they are such even numbers...) but this is mostly a drop in the bucket in the ground scheme of things, so we won't worry about it too much


```{r explore data}
### does larger production mean increased mortality rate?
plot(all_salmon$salmon_kg, all_salmon$mortality_rate) #no

### which counties have higher mortality rates
ggplot(all_salmon)+
  geom_line(aes(x= year, y = mortality_rate, color= region))

salmon_model <- lm(delivered_for_sale_count ~salmon_tonnes, data = all_salmon)
salmon_model
summary(salmon_model)
plot(salmon_model)

ggplot(all_salmon) +
  geom_point(aes(x= salmon_tonnes, y = delivered_for_sale_count))+
  xlab("Tonnage of Salmon") +
  ylab("Number Salmon Sold") +
  theme_classic() +
  stat_smooth(aes(x= salmon_tonnes, y = delivered_for_sale_count), method = "lm")

plot(all_salmon$loss_count, all_salmon$delivered_for_sale_count)
```

Simple model conversion production to numbers
tanding_stock_beginning_year ~ number_produced/sold - 1
```{r conversion production to numbers}

salm_conv_model <- lm(Stock_Jan1_count ~ delivered_for_sale_count - 1, data = test)
salm_conv_model
summary(salm_conv_model)

ggplot(all_salmon)+
  geom_point(aes(x= delivered_for_sale_count, y = Stock_Jan1_count)) + 
  geom_abline(intercept=0, slope = 1.477)
```



Making histogram graphs for harvest weights 
- mean and standard deviations

```{r}

all_salmon_2 <- all_salmon %>% 
  mutate(sd = sd(avg_harvest_wgt_kg),
         mean = mean(avg_harvest_wgt_kg))


hist_harv_weight <- ggplot(all_salmon) +
  geom_histogram(aes(x= avg_harvest_wgt_kg), fill = "gray65") +
  ggtitle("Norwegian Salmon Harvest Weight") +
  ylab("Count") +
  xlab("Harvest Weight (kg)") +
  theme_classic() +
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg)) ,col='dodgerblue2',size=1)+
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg) + sd(avg_harvest_wgt_kg)), col='seagreen3', size = 0.5)+
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg) - sd(avg_harvest_wgt_kg)), col='seagreen3', size = 0.5)+
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg) - 2*sd(avg_harvest_wgt_kg)), col='seagreen3', size = 0.5)+
  geom_vline(aes(xintercept = mean(avg_harvest_wgt_kg) + 2*sd(avg_harvest_wgt_kg)), col='seagreen3', size = 0.5) +
  theme(legend.position = "none") 
  
hist_harv_weight

mean(all_salmon$avg_harvest_wgt_kg)
#4.907344
sd(all_salmon$avg_harvest_wgt_kg)
#0.3927127
min(all_salmon$avg_harvest_wgt_kg)
#3.30712
max(all_salmon$avg_harvest_wgt_kg)
#6.53237

```




















