---
title: "Rasterizing prodution per each region"
author: "Gage Clawson (UCSB, NCEAS, OHI)"
date: "10/09/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---


In this script we allocated the production per farm (equally if there is no subregional production estimates). 

```{r}

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)

source(here("_spatial/template_raster.R"))


```


# Global regions

```{r}

# this file includes ocean regions:
gadm <- raster("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm36mol_pyfill_10km.tif")

gadm_latlon <- raster::projectRaster(gadm, food_raster, method="ngb", over=TRUE)
plot(gadm_latlon)

gadm_codes <- read.csv("/home/shares/food-systems/Food_footprint/_raw_data/Country_regions/gadm_reg_codes.csv") %>% 
  mutate(reg_id = as.numeric(reg_id))

```

# read in points and converted to spatial dataframe
```{r}

all_farms <- read_csv("data/all_marine_aquaculture_farms_sources_final.csv") %>%
      st_as_sf(., 
           coords = c("X", "Y"),
           crs = crs(food_raster), 
           agr = "constant")  


bivalve_farms <- all_farms %>%
  filter(species_group == "Unfed or algae fed bivalve molluscs")


```


# determine subregions where points are located

```{r}

bivalve_farms$reg_id <- raster::extract(gadm_latlon, bivalve_farms) 

farms_sf <- bivalve_farms %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1)) 

farms_sf$check <-  paste(farms_sf$iso3c, farms_sf$GID_0, sep=":")
table(farms_sf$check)

mapview(farms_sf)
# some annoying mismatches due to raster resolution. Fix these

# CHN:HKG
# CHN:MAC
# CHN:PRK
# CHN:TWN
# CHN:VNM
# HKG:CHN
# IRL:GBR
# KHM:VNM
# NLD:DEU
# SVN:HRV
# TWN:CHN
# USA:CAN

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:HKG", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:HKG", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "CHN:MAC", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:MAC", "China", NAME_0)) %>%
    mutate(GID_0 = ifelse(check %in% "CHN:PRK", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:PRK", "China", NAME_0)) %>%
      mutate(GID_0 = ifelse(check %in% "CHN:TWN", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:TWN", "China", NAME_0)) %>%
      mutate(GID_0 = ifelse(check %in% "CHN:VNM", "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CHN:VNM", "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "HKG:CHN", "HKG", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "HKG:CHN", "Hong Kong", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "IRL:GBR", "IRL", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "IRL:GBR", "Ireland", NAME_0)) %>% 
    mutate(GID_0 = ifelse(check %in% "KHM:VNM", "KHM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "KHM:VNM", "Cambodia", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "NLD:DEU", "NLD", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "NLD:DEU", "Netherlands", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "SVN:HRV", "SVN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "SVN:HRV", "Slovenia", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "TWN:CHN", "TWN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "TWN:CHN", "Taiwan", NAME_0)) %>%  
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0))  
  
farms_sf_correct$check <-  paste(farms_sf_correct$iso3c, farms_sf_correct$GID_0, sep=":")
table(farms_sf_correct$check)




mapview(farms_sf_correct) # this all looks reasonable, no crazy points
```


# FAO salmon production data per country
```{r}

fao <- read.csv(here("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(iso3c, fao_tonnes_production)

```


# join country production to farms by iso3c

```{r}

farms_sf_correct <- farms_sf_correct %>%
  left_join(fao, by="iso3c")

summary(farms_sf_correct) # make sure no production NA values

```

# get areas with no regional production data and calculate production per farm

```{r}

## calculate farm production
farms_prod <- farms_sf_correct %>%
  group_by(NAME_0) %>%
  add_tally() %>%
  ungroup() %>%
  # mutate(tonnes_per_farm = fao_tonnes_production/n) %>%
  dplyr::select(iso3c, tonnes_per_farm, geometry)

farms_sf_prod <- st_as_sf(farms_prod)

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/updated/prod_data_by_cell_iso3c.shp", delete_dsn = TRUE) ## overwrite file if already there

```

# combine and check it all matches ok

```{r}

test <- farms_prod %>%
  st_drop_geometry() %>%
  group_by(iso3c) %>%
  summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao) %>%
  mutate(difference = fao_tonnes_production - total_tonnes)


```

## convert to raster, with the value of each cell equalling the sum tonnes per farm for all farms landing in cell.

```{r}

farms_sf <- st_as_sf(farms_prod)
mapview(farms_sf)

bivalve_raster_check <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum)
mapview(bivalve_raster_check)

bivalve_raster <- rasterize(farms_sf, food_raster, field = "tonnes_per_farm", fun=sum, background=0)
plot(log(bivalve_raster + 1))

bivalve_raster_df <- as.data.frame(bivalve_raster, xy=TRUE) %>%
  dplyr::select(x,y, tonnes_production=layer)

cellStats(bivalve_raster, stat = "sum") # 17436803
sum(bivalve_raster_df$tonnes_production) # 17436803
sum(farms_sf$tonnes_per_farm, na.rm = TRUE) # 17436803
sum(fao$fao_tonnes_production) # 17435623 - slightly off? 

write_csv(bivalve_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/updated/bivalve_farm_updated.csv")

```
